### 2021-02-14 articles/article.tex
Initial commit

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Set page geometry
\usepackage[margin=2.5cm,headsep=0.5cm]{geometry}

\input{../preamblex}

\begin{document}

Nicholas Kostin \\
\url{https://github.com/nicholaskostin}

\section{Introduction}

This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist. Rather, what follows is an incoherent collection of examples that demonstrate good practice. Be sure to visit \url{https://github.com/nicholaskostin/LaTeX-templates} for more.

\section{Eigenvalues of a Hermitian Operator}

It is not hard to show that the eigenvalues of a Hermitian operator are real. Let $\ket{a}$ be an eigenstate of the Hermitian operator $A$ corresponding to eigenvalue $a$, then
\begin{equation}
    A \ket{a} = a \ket{a}. \label{eq:quantum:eigenvalueproblem}
\end{equation}

Then we have
\begin{equation}
    \braket{a|A|a} = \braket{a|a|a} = a\braket{a|a}. \label{eq:quantum:1}
\end{equation}

Taking the Hermitian conjugate of both sides of (\ref{eq:quantum:eigenvalueproblem}) gives
\begin{equation}
    \bra{a} A^{\dagger} = a^{*} \bra{a}.
\end{equation}

Then we also have
\begin{equation}
    \braket{a|A^{\dagger}|a} = a^{*} \braket{a|a} \label{eq:quantum:2}
\end{equation}

Since $A$ is Hermitian, we have $\braket{a|A^{\dagger}|a} = \braket{a|A|a}$. Then comparing (\ref{eq:quantum:1}) and (\ref{eq:quantum:2}) gives
\begin{equation*}
    \left( a - a^* \right) \braket{a|a} = 0.
\end{equation*}

This, of course, implies that $a = a^*$, since $\braket{a|a} \neq 0$. Then it must be the case that $a$ is real.

\section{Unit Basis Vectors}

Let $\ihat$, $\jhat$, and $\khat$ be unit vectors parallel to the $x$, $y$, and $z$ axes, respectively. An arbitrary vector $\bm{a}$ can be expanded in terms of these \emph{basis vectors}:
\begin{equation}
    \bm{a} = a_x \ihat + a_y \jhat + a_z \khat.
\end{equation}

One can label a point $P$ by its Cartesian coordinates $(x, y, z)$, but sometimes it is more convenient to use \emph{spherical} coordinates $(r, \theta, \phi)$; $r$ is the distance from the origin (the magnitude of the position vector $\bm{r}$), $\theta$ (the angle down from the $z$-axis) is called the \emph{polar angle}, and $\phi$ (the angle around from the $x$-axis) is the \emph{azimuthal angle}. The unit vectors $\rhat$, $\thetahat$, $\phihat$ constitute an orthogonal basis set. In terms of the Cartesian unit vectors,
\begin{equation}
    \begin{rcases} \displaystyle \rhat = \sin{\theta}\cos{\phi}\ \ihat + \sin{\theta}\sin{\phi}\ \jhat + \cos{\theta}\ \khat, \\ \displaystyle \thetahat = \cos{\theta}\cos{\phi}\ \ihat + \cos{\theta}\sin{\phi}\ \jhat - \sin{\theta}\ \khat, \\ \displaystyle \phihat = -\sin{\phi}\ \ihat + \cos{\phi}\ \jhat. \end{rcases}
\end{equation}

Finally, one can label a point $P$ by its cylindrical coordinates $(\rho, \phi, z)$; $\phi$ has the same meaning as in spherical coordinates, and $z$ is the same as Cartesian, but $\rho$ is the distance to $P$ from the $z$-axis. The unit vectors are
\begin{equation}
    \begin{rcases} \displaystyle \rhohat = \cos{\phi}\ \ihat + \sin{\phi}\ \jhat, \\ \displaystyle \phihat = -\sin{\phi}\ \ihat + \cos{\phi}\ \jhat, \\ \displaystyle \zhat = \khat. \end{rcases}
\end{equation}

\section{Awesome Circled Numbers}

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=1.6]
    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
    {
        \node at (\c,0) {\Huge\circled{\c}{TEAL}{RED}{BLACK}};
    }
\end{tikzpicture}
\caption*{Here are some cool circled numbers. The first argument is whatever is to be circled, and the second argument is the background color. The third argument is the outline color, and the fourth argument is the color of the first argument.}
\end{figure}

These circled numbers work in equations too!

\begin{equation*}
    \Scale[6]{\circled{4}{TEAL}{RED}{BLACK} + \circled{4}{TEAL}{RED}{BLACK} = \circled{8}{TEAL}{RED}{BLACK}}
\end{equation*}

\section{Consider a Graph}

Consider a graph with vertices

\begin{equation*}
    V = \left\{ 1, 2, 3, 4, 5, 6 \right\}
\end{equation*}

and edges
\begin{equation*}
    E = \left\{ 1 \to 2, 1 \to 3, 1 \to 4, 2 \to 1, 2 \to 3, 3 \to 4, 4 \to 1, 4 \to 3, 4 \to 5, 4 \to 6, 5 \to 6, 6 \to 5 \right\}
\end{equation*}

The directed graph for this vertex set $V$ and edge set $E$ is

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{DARKBLUE}{red}{red}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{DARKBLUE}{red}{red}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{DARKBLUE}{red}{red}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{DARKBLUE}{red}{red}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{DARKBLUE}{red}{red}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{DARKBLUE}{red}{red}};
    %
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

\section{Classical Electromagnetism}

Here are the Maxwell equations:

\begin{equation*}
    \begin{cases} \displaystyle \nabla \cdot \bm{E} = \frac{\rho}{\epsilon_o} \\ \displaystyle \nabla \cdot \bm{B} = 0 \\ \displaystyle \nabla \times \bm{E} = -\frac{\partial\bm{B}}{\partial t} \\ \displaystyle \nabla \times \bm{B} = \mu_o \bm{J} + \mu_o\epsilon_o \frac{\partial\bm{E}}{\partial t} \end{cases}.
\end{equation*}

The Lorentz force law reads
\begin{equation*}
    \bm{F} = q \left( \bm{E} + \bm{v} \times \bm{B} \right).
\end{equation*}

Finally, most experts agree that
\begin{equation*}
    \bm{E} = -\nabla V - \frac{\partial \bm{A}}{\partial t}, \qquad \text{and} \qquad \bm{B} = \nabla \times \bm{A}.
\end{equation*}

\section{Matrix Multiplication}

Consider some $A \in \bbR^{p \times q}$ and $B \in \bbR^{q \times p}$. We can represent these matrices as
\begin{equation*}
    A = \begin{pmatrix} a_{11} & a_{12} & \cdots & a_{1q} \\ a_{21} & a_{22} & \cdots & a_{2q} \\ \vdots & \vdots & \ddots & \vdots \\ a_{p1} & a_{p2} & \cdots & a_{pq} \end{pmatrix} \qquad \text{and} \qquad B = \begin{pmatrix} b_{11} & b_{12} & \cdots & b_{1p} \\ b_{21} & a_{22} & \cdots & b_{2p} \\ \vdots & \vdots & \ddots & \vdots \\ b_{q1} & b_{q2} & \cdots & b_{qp} \end{pmatrix}
\end{equation*}

respectively. Then the product $AB$ can be written
\begin{equation*}
    AB = \begin{pmatrix} a_{11} b_{11} + \cdots + a_{1q} b_{q1} & a_{11} b_{12} + \cdots + a_{1q} b_{q2} & \cdots & a_{11} b_{1p} + \cdots + a_{1q} b_{qp} \\ a_{21} b_{11} + \cdots + a_{2q} b_{q1} & a_{21} b_{12} + \cdots + a_{2q} b_{q2} & \cdots & a_{21} b_{1p} + \cdots + a_{2q} b_{qp} \\ \vdots & \vdots & \ddots & \vdots \\ a_{p1} b_{11} + \cdots + a_{pq} b_{q1} & a_{p1} b_{12} + \cdots + a_{pq} b_{q2} & \cdots & a_{p1} b_{1p} + \cdots + a_{pq} b_{qp} \end{pmatrix}.
\end{equation*}

\section{Electric Fields on Pointy Things}

The pointy bits on a conducting surface should produce greater electric fields then the flat bits. Let's show that numerically. Laplace's equation, in two dimensions, reads
\begin{equation}
    \nabla^2 V = \frac{\partial^2 V}{\partial x^2} + \frac{\partial^2 V}{\partial y^2} = 0.
\end{equation}

We can solve Laplace's equation numerically using a finite difference method for a rectangular region. That is, we partition a rectangle into a lattice of grid points. If the spacing in the $x$-direction is $\Delta x$, the second derivative $\frac{\partial^2 V}{\partial x^2}$ is
\begin{equation}
    \frac{\partial^2 V}{\partial x^2} = \frac{V(x + \Delta x, y) - 2V(x,y) + V(x - \Delta x, y)}{\Delta x^2}.
\end{equation}

Similarly, if the spacing in the $y$-direction is $\Delta y$, the second derivative $\frac{\partial^2 V}{\partial y^2}$ is
\begin{equation}
    \frac{\partial^2 V}{\partial y^2} = \frac{V(x, y + \Delta y) - 2V(x,y) + V(x, y - \Delta y)}{\Delta y^2}.
\end{equation}

For convenience, let's say $\Delta x = \Delta y = h$. The Laplacian operator in two-dimensions becomes
\begin{equation}
    \frac{\partial^2 V}{\partial y^2} + \frac{\partial^2 V}{\partial y^2} = \frac{V(x + h, y) + V(x - h, y) + V(x, y + h) + V(x, y - h) - 4V(x,y)}{h^2}.
\end{equation}

Then Laplace's equation becomes
\begin{gather}
    V(x + h, y) + V(x - h, y) + V(x, y + h) + V(x, y - h) - 4V(x,y) = 0 \\
    \implies \boxed{V(x,y) = \frac{V(x + h, y) + V(x - h, y) + V(x, y + h) + V(x, y - h)}{4}}.
\end{gather}

That is, the potential $V(x,y)$ is the average of its four neighboring points on the lattice. Let's make this concrete by drawing a diagram.

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[xscale=1,yscale=1]
    % Draw outside rectangle
    \draw[black] (-2,-2) rectangle (14,10);
    % Draw lattice points
    \foreach \a in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12}
    {
        \foreach \b in {0, 1, 2, 3, 4, 5, 6, 7, 8}
        {
            \filldraw[BLACK] (\a, \b) circle (2pt);
        }
    }
    \node[BLACK, anchor=north] at (0,0) {$x_0$};
    \node[BLACK, anchor=north] at (1,0) {$x_1$};
    \node[BLACK, anchor=north] at (11,0) {$x_{N - 1}$};
    \node[BLACK, anchor=north] at (12,0) {$x_N$};
    \node[BLACK, anchor=east] at (0,0) {$y_0$};
    \node[BLACK, anchor=east] at (0,1) {$y_1$};
    \node[BLACK, anchor=east] at (0,7) {$y_{M - 1}$};
    \node[BLACK, anchor=east] at (0,8) {$y_M$};
    \draw[BLACK, <->] (7,-0.2) -- (8,-0.2);
    \node[BLACK, below] at (7.5,-0.2) {$h$};
    \draw[BLACK, <->] (-0.2,4) -- (-0.2,5);
    \node[BLACK, left] at (-0.2,4.5) {$h$};
    \filldraw[RED] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
    \draw[RED] (6,3) -- (6,4) -- (6,5);
    \draw[RED] (5,4)-- (6,4) -- (7,4);
    \filldraw[BLUE] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
    \filldraw[BLUE] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
    \filldraw[BLUE] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
    \filldraw[BLUE] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
    \draw[BLACK, <->] (0,8.3) -- (12,8.3);
    \node[BLACK, above] at (6,8.3) {$w$};
    \draw[BLACK, <->] (12.3,0) -- (12.3,8);
    \node[BLACK, right] at (12.3,4) {$\ell$};
\end{tikzpicture}
\caption{A two-dimensional lattice of points.}
\label{fig:latticegrid}
\end{figure}

As shown in Fig. (\ref{fig:latticegrid}), we partition the interval $0 < x < w$ into $N + 1$ evenly spaced points. That is,
\begin{equation}
    x_n = nh, \qquad \text{for} \quad n \in \left\{ 0, 1, \dots, N \right\}.
\end{equation}

Likewise, we divide the interval $0 < y < \ell$ into $M + 1$ evenly spaced points. That is,
\begin{equation}
    y_m = mh, \qquad \text{for} \quad m \in \left\{ 0, 1, \dots M \right\}.
\end{equation}

Shown on the following pages is the implementation of this numerical method.

% If we were uploading from an external file, use the line below.
% \lstinputlisting[language=python]{corners.py}

\begin{lstlisting}[language=Python]
"""
Created on Mon Feb 03 13:12:20: 2020
Author: Nicholas D. Kostin
Description: Numerical solution to Laplace's equation for a rectangle
"""

import numpy as np, matplotlib.pyplot as plt

plt.rcParams['mathtext.fontset'] = 'stix'
plt.rcParams['font.family'] = 'STIXGeneral'

# Physical constants
eps0 = 8.85e-12 # permittivity of free space

# Dimensions of region
region_width = 120 # Horizontal length of region
region_length = 80  # Vertical length of region

# Dimensions of conucting rectangle
rectangle_width = 60  # Horizontal length of conducting rectangle
rectangle_length = 40  # Vertical length of conducting rectangle

# Location of bottom-left corner of conducting rectangle
rect_corner = 20

# Set potential at boundaries of region to be zero
boundary_potential = 0

# Dirichlet Boundary conditions on conducting rectangle
# All sides at the same potential
V_box = 9

# Set color interpolation and color map
color_interpolation = 20
color_map = plt.cm.coolwarm # dope-ass colors

# Create lattice of points
X, Y = np.meshgrid(np.arange(0, region_width), np.arange(0, region_length))

# Set array size and the interior value with some guess
V = np.ones((region_length, region_width))
V.fill(0)

# Set potential at boundaries of region
V[1, :] = boundary_potential # potential at bottom
V[region_length - 1, :] = boundary_potential # potential at top
V[:, 1] = boundary_potential # potential at left
V[:, region_width - 1] = boundary_potential # potential at right

# Set potential at boundaries of conducting rectangle
V[rect_corner, rect_corner:rect_corner + rectangle_width] = V_box # potential at bottom
V[rect_corner + rectangle_length, rect_corner:rect_corner + rectangle_width] = V_box # potential at top
V[rect_corner:rect_corner + rectangle_length, rect_corner] = V_box # potential at left
V[rect_corner:rect_corner + rectangle_length, rect_corner + rectangle_width] = V_box # potential at right

# Implement 1000 iterations (and hope that's enough for convergence)
for iteration in range(0,1000):
    for i in range(1, region_length - 1, 1):
        for j in range(1, region_width - 1, 1):
            # Conducting surfaces are equipotentials
            if rect_corner <= i <= rect_corner + rectangle_length and rect_corner <= j <= rect_corner + rectangle_width:
                V[i, j] = V[i, j]
            # Implement finite difference method                
            else:
                V[i, j] = (1/4) * (V[i - 1][j] + V[i + 1][j] + V[i][j - 1] + V[i][j + 1])

# Create array for electric field
E = np.zeros((region_length, region_width, 2))

# Compute electric field
for i in range (region_length):
    for j in range (region_width):
        # Electric field is zero inside a conductor
        if rect_corner <= i <= rect_corner + rectangle_length and rect_corner <= j <= rect_corner + rectangle_width:
            E[i, j] = [0, 0]
        # Electric field is derivative of potential otherwise
        elif i != 0 and i != region_length - 1 and j != 0 and j != region_width - 1:
            E[i, j] = [(V[i + 1, j] - V[i - 1, j])/(2), (V[i, j + 1] - V[i, j - 1])/(2)]

# Create array for magnitude of the electric field
E_magnitude = np.zeros((region_length, region_width))

# Compute the magnitude of the elctric field
for i in range (region_length):
    for j in range (region_width):
        E_magnitude[i, j] = (E[i, j, 0]**2 + E[i, j, 1]**2)**(1/2)

# Plot a contour map of the potential
plt.figure(1)
plt.title("Contour of Potential")
plt.contourf(X, Y, V, color_interpolation, cmap=color_map)
plt.colorbar() # Set colorbar
plt.show() # Display the color map

# Plot a contour map of the electric field magnitude
plt.figure(2)
plt.title("Contour of Magnitude of Electric Field")
plt.contourf(X, Y, E_magnitude, color_interpolation, cmap=color_map)
plt.colorbar() # Set colorbar
plt.show() # Display the color map
\end{lstlisting}

\section{Infinite Square Well Potential}

Suppose we have a quantum particle with mass $m$ in an infinite square well potential:
\begin{equation*}
    V(x) = \begin{cases} 0, & 0 \leqslant x \leqslant \infty \\ \infty & \text{otherwise} \end{cases}.
\end{equation*}

The expectation value of the position $\hat{x}$ of the particle measured in the energy eigenstate $\ket{\psi_n}$ that is represented by $\psi_n(x) = \sqrt{\frac{2}{\pi}} \sin{(nx)}$, we use
\begin{equation}
    \Braket{\psi_n | \hat{x} | \psi_n} = \int_{0}^{\pi} \psi_n^*(x)\ x\ \psi_n(x)\ dx = \frac{2}{\pi} \int_{0}^{\pi} x\ \sin^2{(nx)}\ dx = \frac{\pi}{2}.
\end{equation}

The expectation value of the momentum $\hat{p}$ in the eigenstate $\ket{\psi_n}$ is given by
\begin{equation}
    \Braket{\psi_n | \hat{p} | \psi_n} = \int_{0}^{\pi} \psi_n^*(x)\ \left( -i\hbar\frac{d}{dx} \right)\ \psi_n(x)\ dx = 0.
\end{equation}

\section{Commuting Hermitian Matrices}

Let $A, B \in \bbC^{p \times p}$ be Hermitian matrices. Prove that $AB$ is Hermitian if and only if $A$ and $B$ commute (\textit{i.e.} they don't work from home).

\begin{proof}

A matrix $\mathscr{A} \in \bbC^{p \times p}$ is Hermitian if it satisfies
\begin{equation*}
    \mathscr{A}^{\dagger} = \mathscr{A}.
\end{equation*}

That is, a matrix $\mathscr{A} \in \bbC^{p \times p}$ is Hermitian if it is its own conjugate transpose. Moreover, for $\mathscr{A} \in \bbC^{p \times q}$ and $\mathscr{B} \in \bbC^{q \times r}$, we have the identity
\begin{equation*}
    \left( \mathscr{AB} \right)^{\dagger} = \mathscr{B}^{\dagger} \mathscr{A}^{\dagger}.
\end{equation*}

We will start by proving the forward direction. That is, we will show that if $A$ and $B$ commute, then $AB$ must be Hermitian. Using the identity above to take the conjugate transpose of $AB$ we get
\begin{equation*}
    \left( AB \right)^{\dagger} = B^{\dagger} A^{\dagger}.
\end{equation*}

But since we assumed $A$ and $B$ to both be Hermitian, we have that $B^{\dagger} = B$ and $A^{\dagger} = A$. Explicitly,
\begin{equation*}
    \left( AB \right)^{\dagger} = B^{\dagger} A^{\dagger} = BA.
\end{equation*}

But since we assumed $A$ and $B$ commute, then $BA = AB$. And we have
\begin{equation*}
    \left( AB \right)^{\dagger} = B^{\dagger} A^{\dagger} = BA = AB
\end{equation*}

Thereby $AB$ satisfies the definition of a Hermitian matrix. Now we will show the reverse direction: that if $AB$ is Hermitian then $A$ and $B$ must necessarily commute. If $AB$ is Hermitian, then
\begin{equation*}
    \left( AB \right)^{\dagger} = AB
\end{equation*}

But we already showed that we can rewrite the left-hand side of the equation above as $\left( AB \right)^{\dagger} = B^{\dagger} A^{\dagger} = AB$, since we assumed $A$ and $B$ to both be Hermitian. Then we have
\begin{equation*}
    BA = AB.
\end{equation*}

And clearly, $A$ and $B$ must necessarily commute.

\end{proof}

\section{Blind Text}

\blindtext[1]

\section{Some Results from Real Analysis}

Here we have a \emph{theorem}.

\begin{theorem}[Bolzano-Weierstrass]
Every bounded sequence has a convergent subsequence.
\end{theorem}

What follows is a \emph{lemma}.

\begin{lemma}
Cauchy sequences are bounded.
\end{lemma}

\section{Computer Colors}

HTML color codes are hexadecimal triplets representing the colors red, green and blue.

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=1.2]
    % primary colors
    \fill[BLUE] (30:2.4) circle (4);
    \fill[RED] (150:2.4) circle (4);
    \fill[GREEN] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[PURPLE] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[YELLOW] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[TEAL] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[WHITE] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}

\end{document}

### 2021-02-14 homework/hmwks/hmwk1.tex
Initial commit

\documentclass[class=report,crop=false]{standalone}
\usepackage[margin=2.5cm,headsep=0.5cm]{geometry}
\input{../preamble}

\begin{document}

\section*{A Vector in a Hilbert space}
\addtocounter{section}{1}
\addcontentsline{toc}{section}{A Vector in a Hilbert space}
\setcounter{equation}{0}

The state of a quantum system can be described by a vector in a Hilbert space. Once a basis is chosen for the Hilbert space, the quantum state can be represented by a column vector with complex number entries. Using a column vector to describe a quantum state has the drawbrack of being basis-dependent. Suppose the basis of a Hilbert space is formed by $\displaystyle \left\{ \chi_1, \chi_2, \cdots, \chi_N \right\}$. We now have two ways to represent a quantum state.

\begin{equation}
    \ket{\psi} = \sum\limits_{i = 1}^{N} a_i \ket{\chi_i} \qquad \Longleftrightarrow \qquad \bm{\psi} = \begin{pmatrix} a_1 \\ \vdots \\ a_N \end{pmatrix}
\end{equation}

\section*{The Inner Product}
\addtocounter{section}{1}
\addcontentsline{toc}{section}{The Inner Product}
\setcounter{equation}{0}

For two real column vectors $\bm{u}$ and $\bm{v}$, the inner product between them is defined as $\displaystyle \bm{u}^T \bm{v} = \sum_i u_i v_i$. This is the same as the dot product between the two corresponding vectors in the Euclidean space $\vec{u} \cdot \vec{v}$. The dot product is invariant under a change of basis. For two vectors in the Hilbert space $\ket{\psi}$ and $\ket{\phi}$, we denote their inner product as $\braket{\psi | \phi}$. If a specific basis of the Hilbert space is chosen, we can represent $\ket{\psi}$ and $\ket{\phi}$ using two column vectors:
\begin{equation}
    \bm{\psi} = \begin{pmatrix} a_1 \\ \vdots \\ a_n \end{pmatrix} \qquad \text{and} \qquad \bm{\phi} = \begin{pmatrix} b_1 \\ \vdots \\ b_n \end{pmatrix}.
\end{equation}

Correspondingly, the bra $\bra{\psi}$ would be represented by the row vector
\begin{equation}
    \bm{\psi}^{\dagger} = \begin{pmatrix} a_1^* \cdots a_n^* \end{pmatrix}.
\end{equation}

The Dirac notation $\braket{\psi|\phi}$ can then be regarded as the matrix product of $\bm{\psi}^{\dagger}$ and $\bm{\phi}$:
\begin{equation}
    \braket{\psi|\phi} = \bm{\psi}^{\dagger}\bm{\phi} = \sum\limits_{i = 1}^{n} a_i^* b_i.
\end{equation}

Note that the inner product is also invariant under the change of basis.

\section*{Orthonormal Basis}
\addtocounter{section}{1}
\addcontentsline{toc}{section}{Orthonormal Basis}
\setcounter{equation}{0}

The basis vectors of a Hilbert space are typically made of states that are normalized and orthogonal to each other. For example, if $\left\{ \chi_1, \chi_2, \cdots, \chi_N \right\}$ form a basis, then for any $i, j \in \left\{ 1, 2, \cdots, N \right\}$, we have
\begin{equation}
    \braket{\chi_i | \chi_j} = \delta_{ij} = \begin{cases} \displaystyle 0, & \text{if } i \neq j \\ \displaystyle 1, & \text{if } i = j \end{cases}
\end{equation}

Such as basis is said to be \emph{orthonormal}.

\section*{Time Evolution}
\addtocounter{section}{1}
\addcontentsline{toc}{section}{Time Evolution}
\setcounter{equation}{0}

For a \colorbox{REDE}{time-independent} Hamiltonian $\hat{H}$, the state of the system at time $t$ is given by the solution to the Schr{\"o}dinger equation $\displaystyle i\hbar \frac{d \ket{\psi(t)}}{dt} = \hat{H} \ket{\psi(t)}$:

\begin{equation}
    \Ket{\psi(t)} = e^{-i\hat{H}t / \hbar} \ket{\psi(0)}.
\end{equation}

\end{document}

### 2021-07-02 articles/article_with_bib.tex
added article with bibliography

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Set page geometry
\usepackage[margin=2.5cm,headsep=0.5cm]{geometry}

\input{../preamblex}

% Bibliography Management
\usepackage[backend=biber,sorting=none]{biblatex}
\addbibresource{ref.bib}

\begin{document}

Nicholas Kostin \\
\url{https://github.com/nkostin4}

\section{Perturbation Theory --- Nondegenerate Case}

Perturbation theory is a useful technique to obtain approcimate solutions to eigenvalue-eigenvector problems that are too complicated to be solved exactly \cite{byronfuller}. Suppose we want to find the eigenvalues and eigenvectors of a self-adjoint operator $A$ which may be split up into the sum of two self-adjoint operators:
\begin{equation*}
    A = A_o + \epsilon A_1
\end{equation*}

We assume that we knwo something about $A_o$. For example, we might know some eigenvalue and its associated eigenvector. We would like to find the corresponding eigenvalue and eigenvector of $A$, given that the influence of $A_o$ is known to be predominant. We have already anticipated this situation be writing the ``perturbing'' operator in the form of $\epsilon A_1$, where $\epsilon$ is some small parameter \cite{byronfuller}.

\section{Radiation}

When charges accelerate, their fields can transport energy irreversibly out to infinity --- a process we call radiation \cite{griffiths}. Let's assume the source is localized near the orgin. Our objective is to calculate the energy it is radiating at time $t_o$. Imagine a gigantic sphere, out at radius $r$. The power passing through its surface is the integral of the Poynting vector:
\begin{equation*}
    P(r, t) = \oint \bm{S} \cdot d\bm{a} = \frac{1}{\mu_o} \oint \left( \bm{E} \times \bm{B} \right) \cdot d\bm{a}.
\end{equation*}

Because electromagnetic ``news" travels at the speed of light, this energy actually left the source at the earlier time $t_o = t - r/c$, so the power radiated is
\begin{equation*}
    P_{\text{rad}} \left( t_o \right) = \lim_{r \to \infty} P \left( r, t_o + \frac{r}{c} \right)
\end{equation*}

(with $t_o$ held constant). This is the energy (per unit time) that is carried away and never comes back \cite{griffiths}.

% Print entire bibliography - title it 'References'
\printbibliography[heading=bibintoc,title={References}]

\end{document}

### 2021-07-03 articles/article_with_bib.tex
finished bibliography work

@@
 \addbibresource{ref.bib}
+\BiblatexSplitbibDefernumbersWarningOff
 
@@
 
+% \tableofcontents
+
+\section{Introduction}
+
+This brief document is meant to show the best paradigm for bibliography management with {\LaTeX}.
+This guide contains examples that touch on perturbation theory, the Aharonov-Bohm effect, and electromagnetic radiation --- all topics in the field of theoretical physics.
+
+\vspace{1em}
+
+On an entirely unrelated note, it is worth remembering that ``one of the biggest issues of modern post-war institutionalized science is that the funding and peer-review mechanism is self-reinforcing \ldots [which] creates a community of "scientists" who are more and more incestuous and generally oblivious not just to other possibilities of inquiry, but don't even have to be aware of their own priors or assumptions.'' \cite{fragile}.
+
 \section{Perturbation Theory --- Nondegenerate Case}
 
-Perturbation theory is a useful technique to obtain approcimate solutions to eigenvalue-eigenvector problems that are too complicated to be solved exactly \cite{byronfuller}.
+Perturbation theory is a useful technique to obtain approximate solutions to eigenvalue-eigenvector problems that are too complicated to be solved exactly \cite{byronfuller}.
 Suppose we want to find the eigenvalues and eigenvectors of a self-adjoint operator $A$ which may be split up into the sum of two self-adjoint operators:
 \begin{equation*}
-    A = A_o + \epsilon A_1
+    A = A_o + \epsilon A_1.
 \end{equation*}
 
-We assume that we knwo something about $A_o$.
+We assume that we know something about $A_o$.
 For example, we might know some eigenvalue and its associated eigenvector.
@@
 We have already anticipated this situation be writing the ``perturbing'' operator in the form of $\epsilon A_1$, where $\epsilon$ is some small parameter \cite{byronfuller}.
+
+\section{The Aharonov-Bohm Effect}
+
+Classically, a particle can't sense potentials, only fields.
+In other words, the actual value of a potential --- whether it be $\bm{A}$ or $\phi$ --- isn't supposed to matter.
+In quantum mechanics, we want to obtain the eigenfunctions describing allowed particle states by solving $H \psi = E \psi$, where the Hamiltonian reads
+\begin{equation*}
+    H = \frac{1}{2m} \left( \frac{\hbar}{i} \nabla - q \bm{A} \right)^2 + q\phi.
+\end{equation*}
+
+Observe that the Hamiltonian is expressed in terms of potentials, not fields.
+It should then stand to reason that a particle whose behavior is governed quantum mechanically can ``sniff'' nearby magnetic fields via the resulting vector potential $\bm{A}$.
+
+\subsection{General Description}
+
+Suppose $\psi'$ is an eigenstate of
+\begin{equation*}
+	H = \frac{\hbar^2}{2m} \nabla^2 + q\psi.
+\end{equation*}
+
+Observe that this Hamiltonian doesn't have a vector potential present.
+Say $\psi'$ is a basis state.
+Now suppose we consider a new region where $\bm{B}$ is zero (so the vector potential $\bm{A}$ is still curl-free), but now there is a non-zero vector potential:
+\begin{equation*}
+	\nabla \times \bm{A} = \bm{0}, \qquad \bm{A} \neq \bm{0}.
+\end{equation*}
+
+In this regime, the eigenstate, say, $\psi$, of this new Hamiltonian can be built from the old $\psi'$ eigenstates. In fact, these differ only by a phase factor:
+\begin{equation*}
+	\psi = e^{ig} \psi', \qquad \text{where } g \equiv \frac{q}{\hbar} \int \bm{A} \cdot d\bm{\ell}.
+\end{equation*}
+
+All of this is pretty abstract, so let's summarize what we have so far: the wavefunctions for particles in a vector potential --- in a region where there is zero $\bm{B}$-field (and maybe even zero $\bm{E}$-field) --- pick up phases when they travel through that region.
+Different phases depending on the paths involved.
+But no problem, right?
+The square magnitude of the new $\psi$ makes the new phase go away, right?
+Unless, we have more than one particle.
+Then we get observable interference that depends on the value of the vector potential.
+
+\subsection{Aharonov and Bohm's Experiment}
+
+Aharonov and Bohm proposed an experiment in which a stream of electrons is split in two, and passes either side of a solenoid \cite{aharonovbohm}.
+A long solenoid has a uniform magnetic field within it, and nearly zero magnetic field outside.
+However, the vector potential $\bm{A}$ at a distance $r$ from the center of the solenoid is not zero.
+In particular,
+\begin{equation*}
+	\bm{A} = \frac{\pi a^2 B}{2\pi r} \phihat,
+\end{equation*}
+
+where $a$ is the radius of the solenoid and $B$ is the magnitude of the magnetic field.
+One of the electron beams in the experiment travels along this vector potential, while the other moves against it.
+As such, there is a phase accumulation:
+\begin{equation*}
+    g = \frac{q}{\hbar} \int \bm{A} \cdot d\bm{\ell} = \frac{q\ \pi a^2\ B}{2\pi\hbar} \int \left( \frac{1}{r}\ \phihat \right) \cdot \left( r\ \phihat\ d\phi \right) = \pm \frac{q\ \pi a^2\ B}{2\hbar}.
+\end{equation*}
+
+Say, the electrons traveling along the vector potential accumulate a positive phase, while the electrons traveling against the vector potential accumulate an equal and opposite negative phase, such that the phase difference is $\displaystyle \frac{q\ \pi a^2\ B}{\hbar}$.
+
+Herein lies the conclusion that Yakir Aharonov and David Bohm reached --- for a charged quantum particle moving though space, it is insufficient to know the local electromagentic field to predict the time evolution of the particle's wavefunction.
+As cool as this is, the Aharonov Bohm effect is nothing more than a special case of the broader geometric phase \cite{aharonovbohm}.
 
@@
 
-Because electromagnetic ``news" travels at the speed of light, this energy actually left the source at the earlier time $t_o = t - r/c$, so the power radiated is
+Because electromagnetic ``news'' travels at the speed of light, this energy actually left the source at the earlier time $t_o = t - r/c$, so the power radiated is
 \begin{equation*}
@@
 
+% Only books bibliography
+\printbibliography[heading=subbibintoc,type=book,title={Books only}]
+
+% Only Physics Resources
+\printbibliography[heading=subbibintoc,keyword={physics},title={Physics-related only}]
+
 \end{document}

### 2021-07-09 articles/good_practice.tex
new articles

--- 2021-02-14 articles/article.tex
@@
 
+\title{Illustrating Good Practice in {\LaTeX}}
+\author{Nicholas D. Kostin}
+\date{July 2021}
+
 \begin{document}
 
-Nicholas Kostin \\
-\url{https://github.com/nicholaskostin}
+\maketitle
 
@@
 This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist.
-Rather, what follows is an incoherent collection of examples that demonstrate good practice.
-Be sure to visit \url{https://github.com/nicholaskostin/LaTeX-templates} for more.
+Rather, what follows is an incoherent collection of examples that illustrate good practice.
+For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.
 
@@
 These circled numbers work in equations too!
-
 \begin{equation*}
-    \Scale[6]{\circled{4}{TEAL}{RED}{BLACK} + \circled{4}{TEAL}{RED}{BLACK} = \circled{8}{TEAL}{RED}{BLACK}}
+    \bigints_{\circled{$a$}{PINK}{BLACK}{BLACK}}^{\circled{$b$}{GOLDC}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{GOLDC}{BLACK}{BLACK}}^{\circled{$a$}{PINK}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{GREEN}{RED}{BLACK}}
 \end{equation*}
@@
     %
-    \node at (vertex1) (nodeV1) {\Huge\circled{1}{DARKBLUE}{red}{red}};
-    \node at (vertex2) (nodeV2) {\Huge\circled{2}{DARKBLUE}{red}{red}};
-    \node at (vertex3) (nodeV3) {\Huge\circled{3}{DARKBLUE}{red}{red}};
-    \node at (vertex4) (nodeV4) {\Huge\circled{4}{DARKBLUE}{red}{red}};
-    \node at (vertex5) (nodeV5) {\Huge\circled{5}{DARKBLUE}{red}{red}};
-    \node at (vertex6) (nodeV6) {\Huge\circled{6}{DARKBLUE}{red}{red}};
+    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
     %
@@
 \centering
-\begin{tikzpicture}[scale=1.2]
+\begin{tikzpicture}[scale=0.75]
     % primary colors

### 2021-07-09 articles/good_practice.tex
useful additions

@@
 
+\begin{table}[H]
+\centering
+\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
+\caption*{Maxwell's equations and their interpretation.}
+\begin{tabular}{@{}c|c@{}}
+\toprule
+Equation & Interpretation \\ \midrule
+{\parbox[c]{0.3\linewidth}{\begin{gather*} \nabla \cdot \bm{E} = \frac{\rho}{\epsilon_o} \end{gather*}}} & {\parbox[c]{0.6\linewidth}{\begin{center} $\bm{E}$-fields with divergence come from charges (electric monopoles).
+\end{center}}} \\ \midrule
+{\parbox[c]{0.3\linewidth}{\begin{gather*} \nabla \cdot \bm{B} = 0 \end{gather*}}} & {\parbox[c]{0.6\linewidth}{\begin{center} $\bm{B}$-fields with divergence don't exist (no magnetic monopoles).
+\end{center}}} \\ \midrule
+{\parbox[c]{0.3\linewidth}{\begin{gather*} \nabla \times \bm{E} = -\frac{\partial \bm{B}}{\partial t} \end{gather*}}} & {\parbox[c]{0.6\linewidth}{\begin{center} $\bm{E}$-fields with curl come from time-varying $\bm{B}$-fields --- and those \emph{only}.
+\end{center}}} \\ \midrule
+{\parbox[c]{0.3\linewidth}{\begin{align*} \nabla \times \bm{B} &= \mu_o \bm{J} + \mu_o \epsilon_o \frac{\partial \bm{E}}{\partial t} \\ &= \mu_o \left( \bm{J} + \bm{J}_D \right) \end{align*}}} & {\parbox[c]{0.6\linewidth}{\begin{center} $\bm{B}$-fields with curl come from currents (moving electric monopoles) and from time-varying $\bm{E}$-fields.
+Sometimes we refer to $\epsilon_o \frac{\partial \bm{E}}{\partial t}$ as displacement current and bundle the $J$'s together.
+\end{center}}} \\ \bottomrule
+\end{tabular}
+\end{table}
+
+In regions of space where there is no charge or current, Maxwell's equations read
 \begin{equation*}
-    \begin{cases} \displaystyle \nabla \cdot \bm{E} = \frac{\rho}{\epsilon_o} \\ \displaystyle \nabla \cdot \bm{B} = 0 \\ \displaystyle \nabla \times \bm{E} = -\frac{\partial\bm{B}}{\partial t} \\ \displaystyle \nabla \times \bm{B} = \mu_o \bm{J} + \mu_o\epsilon_o \frac{\partial\bm{E}}{\partial t} \end{cases}.
+	\begin{rcases} \displaystyle \nabla \cdot \bm{E} = 0,& \qquad \displaystyle \nabla \times \bm{E} = -\frac{\partial \bm{B}}{\partial t}, \\[1em] \displaystyle \nabla \cdot \bm{B} = 0,& \qquad \displaystyle \nabla \times \bm{B} = \mu_o \epsilon_o \frac{\partial \bm{E}}{\partial t}.\quad \end{rcases}
 \end{equation*}
@@
     AB = \begin{pmatrix} a_{11} b_{11} + \cdots + a_{1q} b_{q1} & a_{11} b_{12} + \cdots + a_{1q} b_{q2} & \cdots & a_{11} b_{1p} + \cdots + a_{1q} b_{qp} \\ a_{21} b_{11} + \cdots + a_{2q} b_{q1} & a_{21} b_{12} + \cdots + a_{2q} b_{q2} & \cdots & a_{21} b_{1p} + \cdots + a_{2q} b_{qp} \\ \vdots & \vdots & \ddots & \vdots \\ a_{p1} b_{11} + \cdots + a_{pq} b_{q1} & a_{p1} b_{12} + \cdots + a_{pq} b_{q2} & \cdots & a_{p1} b_{1p} + \cdots + a_{pq} b_{qp} \end{pmatrix}.
+\end{equation*}
+
+\section{Sinusoidal Waves}
+
+A sinusoidal wave assumes the form
+\begin{equation*}
+    g(z,t) = A \cos{\left[ k \left( z - vt \right) + \delta \right]}.
+\end{equation*}
+
+Figure (\ref{fig:sinusoidalwave}) shows this function at $t = 0$.
+The amplitude of the wave is $A$.
+The argument of the cosine is called the phase, and $\delta$ is the phase constant.
+At $z = vt - \delta / k$, the phase is zero; this is known as the ``central maximum.'' Observe that $\delta/k$ is the distance by which the central maximum is ``delayed.'' Finally, $k$ is the wave number; it is related to the wavelength $\lambda$ by the equation
+\begin{equation*}
+    \lambda = \frac{2\pi}{k},
+\end{equation*}
+
+for when $z$ advances by $2\pi/k$, the cosine executes one complete cycle.
+
+\begin{figure}[H]
+\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\centering
+\begin{tikzpicture}[scale=1.1]
+    \draw[BLACK, ->] (-4,0) -- (9,0) node[BLACK, anchor=west] {$z$};
+    \draw[BLACK, ->] (0,-1.4) -- (0,1.4) node[BLACK, anchor=south] {$g(z,0)$};
+    \draw[BLUE, thick] (-4.6,1) cos (-3.6,0);
+    \draw[BLUE, thick] (-3.6,0) sin (-2.6,-1);
+    \draw[BLUE, thick] (-2.6,-1) cos (-1.6,0);
+    \draw[BLUE, thick] (-1.6,0) sin (-0.6,1);
+    \draw[BLUE, thick] (-0.6,1) cos (0.6,0);
+    \draw[BLUE, thick] (0.6,0) sin (1.6,-1);
+    \draw[BLUE, thick] (1.6,-1) cos (2.6,0);
+    \draw[BLUE, thick] (2.6,0) sin (3.6,1);
+    \draw[BLUE, thick] (3.6,1) cos (4.6,0);
+    \draw[BLUE, thick] (4.6,0) sin (5.6,-1);
+    \draw[BLUE, thick] (5.6,-1) cos (6.6,0);
+    \draw[BLUE, thick] (6.6,0) sin (7.6,1);
+    %
+    \draw[BLACK, ->] (3.6,0) -- (3.6,1) node[BLACK, left, midway] {\small $A$};
+    \draw[BLACK] (3.2,1) -- (4.0,1);
+    %
+    \filldraw[BLACK] (-0.6,1) circle (0.1);
+    \node[BLACK, above] at (-3.6,1.3) {\parbox[c]{0.2\textwidth}{\begin{center} \small Central \\ maximum \end{center}}};
+    \draw[BLACK, thick, <-] (-0.7,1.1) -- (-3,2);
+    %
+    \draw[BLACK, dashed] (-0.6,1) -- (-0.6,0);
+	\draw[BLACK, thick, decoration={brace, mirror, raise=5pt}, decorate] (-0.6,0) -- (0,0) node[black, midway, below=6pt] {\small $\delta/k$};
+	%
+	\draw[BLACK, ->] (5,1.6) -- (6.6,1.6) node[BLACK, midway, above] {\small $v$};
+	%
+	\draw[BLACK] (1.6,-1) -- (1.6,-1.5);
+	\draw[BLACK] (5.6,-1) -- (5.6,-1.5);
+	\draw[BLACK, <->] (1.6,-1.25) -- (5.6,-1.25) node[BLACK, midway, below] {\small $\lambda$};
+\end{tikzpicture}
+\caption{A sinusoidal wave train. With the passage of time, the entire wave train proceeds to the right.}
+\label{fig:sinusoidalwave}
+\end{figure}
+
+At any fixed point $z$, the string vibrates up and down, undergoing one full cycle in a period
+\begin{equation*}
+    T = \frac{2\pi}{kv}.
 \end{equation*}
@@
 
-\blindtext[1]
+\blindtext[3]
 

### 2021-07-20 articles/good_practice.tex
tiny change
improved good practice article

@@
 This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist.
-Rather, what follows is an incoherent collection of examples that illustrate good practice.
+Instead, what follows is an incoherent collection of examples that illustrate good practice.
 For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.
@@
 
-\section{Awesome Circled Numbers}
-
-\begin{figure}[H]
-\centering
-\begin{tikzpicture}[scale=1.6]
-    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
-    {
-        \node at (\c,0) {\Huge\circled{\c}{TEAL}{RED}{BLACK}};
-    }
-\end{tikzpicture}
-\caption*{Here are some cool circled numbers.
-The first argument is whatever is to be circled, and the second argument is the background color.
-The third argument is the outline color, and the fourth argument is the color of the first argument.}
-\end{figure}
-
-These circled numbers work in equations too!
-\begin{equation*}
-    \bigints_{\circled{$a$}{PINK}{BLACK}{BLACK}}^{\circled{$b$}{GOLDC}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{GOLDC}{BLACK}{BLACK}}^{\circled{$a$}{PINK}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{GREEN}{RED}{BLACK}}
-\end{equation*}
-
 \section{Consider a Graph}
@@
 \end{figure}
+
+\newpage
 
@@
 
-\blindtext[3]
+\blindtext[2]
+
+\newpage
 
@@
 \centering
-\begin{tikzpicture}[scale=0.75]
+\begin{tikzpicture}[scale=0.5]
     % primary colors
@@
 
+\section{Awesome Circled Numbers and Highlighting}
+
+Here are some cool circled numbers.
+The first argument is whatever is to be circled, and the \colorbox{TEAL}{second argument} is the background color.
+The \colorbox{PURPLE}{third argument} is the outline color, and the \colorbox{RED}{fourth argument} is color of the first argument.
+
+\begin{figure}[H]
+\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\centering
+\begin{tikzpicture}[scale=1.6]
+    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
+    {
+        \node at (\c,0) {\Huge\circled{\c}{TEAL}{PURPLE}{RED}};
+    }
+\end{tikzpicture}
+\caption*{Isn't this cool?}
+\end{figure}
+
+These circled numbers work in equations too!
+\begin{equation*}
+    \bigints_{\circled{$a$}{PINK}{BLACK}{BLACK}}^{\circled{$b$}{GOLDC}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{GOLDC}{BLACK}{BLACK}}^{\circled{$a$}{PINK}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{GREEN}{RED}{BLACK}}
+\end{equation*}
+
 \end{document}

### 2021-07-20 homework/hmwks/hmwk1.tex
fixed unnecessary thingy

@@
 
-For a \colorbox{REDE}{time-independent} Hamiltonian $\hat{H}$, the state of the system at time $t$ is given by the solution to the Schr{\"o}dinger equation $\displaystyle i\hbar \frac{d \ket{\psi(t)}}{dt} = \hat{H} \ket{\psi(t)}$:
+For a time-independent Hamiltonian $\hat{H}$, the state of the system at time $t$ is given by the solution to the Schr{\"o}dinger equation $\displaystyle i\hbar \frac{d \ket{\psi(t)}}{dt} = \hat{H} \ket{\psi(t)}$:
 

### 2021-08-07 curriculum_vitae/resume.tex
started resume

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Set page geometry
\usepackage[margin=1.5cm,headsep=0.5cm]{geometry}

\input{../preamblex}

\begin{document}

\begin{minipage}{0.63\textwidth}
\begin{flushleft}
\textbf{\textsc{\Huge{Nicholas D. Kostin}}}
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.35\textwidth}
\begin{flushright}
\parbox[c]{\textwidth}{Website: \url{https://nkostin.xyz} \\ Email: \texttt{contact@nkostin.xyz} \\ GitHub: \url{https://github.com/nkostin4} \\ Mobile: +1 719-271-9108}
\end{flushright}
\end{minipage}

\vspace{1em}

\textbf{\Large{Education}} \\[-0.5em]
\rule{\textwidth}{1pt}

\hspace{1.5em} \textbf{Colorado School of Mines} \hfill Golden, CO

\hspace{1.5em} Major: \textbf{Engineering Physics} \hfill BS May 2022

\hspace{1.5em} Minor: \textbf{Computational and Applied Mathematics}

\vspace{1em}

\hspace{1.5em} Major GPA: \textbf{4.00} / Cumulative GPA: \textbf{4.00}

\vspace{1em}

\textbf{\Large{Work Experience}} \\[-0.5em]
\rule{\textwidth}{1pt}

\hspace{1.5em} \textbf{Teaching Assistant} \hfill Golden, CO

\hspace{1.5em} \textit{Physics II --- Electromagnetism and Optics} \hfill January 2019 --- May 2021

\end{document}

### 2021-09-06 articles/good_practice.tex
added header and footer
fixed order of sections
minor change
keeping things up to date
twenty third payload
major improvement and fixes

@@
 
+% Continuous per-section numbering of figures and tables
+\usepackage{chngcntr}
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+
 \title{Illustrating Good Practice in {\LaTeX}}
 \author{Nicholas D. Kostin}
-\date{July 2021}
+\date{October 2021}
+
+\usepackage{fancyhdr,lastpage}
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{Illustrating Good Practice in {\LaTeX}}
+\rhead{Nicholas D. Kostin}
+\lfoot{\texttt{https://nkostin.xyz}}
+\rfoot{\thepage\ of \pageref{LastPage}}
 
@@
 
-\section{Consider a Graph}
-
-Consider a graph with vertices
-
-\begin{equation*}
-    V = \left\{ 1, 2, 3, 4, 5, 6 \right\}
-\end{equation*}
-
-and edges
-\begin{equation*}
-    E = \left\{ 1 \to 2, 1 \to 3, 1 \to 4, 2 \to 1, 2 \to 3, 3 \to 4, 4 \to 1, 4 \to 3, 4 \to 5, 4 \to 6, 5 \to 6, 6 \to 5 \right\}
-\end{equation*}
-
-The directed graph for this vertex set $V$ and edge set $E$ is
-
-\begin{figure}[H]
-\centering
-\begin{tikzpicture}
-    \coordinate (vertex1) at (4,0);
-    \coordinate (vertex2) at (2,3.464102);
-    \coordinate (vertex3) at (-2,3.464102);
-    \coordinate (vertex4) at (-4,0);
-    \coordinate (vertex5) at (-2,-3.464102);
-    \coordinate (vertex6) at (2,-3.464102);
-    %
-    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
-    %
-    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
-    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
-    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
-    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
-    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
-    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
-    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
-    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
-\end{tikzpicture}
-\end{figure}
-
-\newpage
-
 \section{Classical Electromagnetism}
@@
 \captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
-\caption*{Maxwell's equations and their interpretation.}
+\caption{Maxwell's equations and their interpretation.}
 \begin{tabular}{@{}c|c@{}}
@@
 
-Shown on the following pages is the implementation of this numerical method.
+What follows is the implementation of this numerical method.
 
@@
 
+Don't forget, however, that too much color is cringe, so be exercise caution!
+
+\section{Consider a Graph}
+
+Consider a graph with vertices
+
+\begin{equation*}
+    V = \left\{ 1, 2, 3, 4, 5, 6 \right\}
+\end{equation*}
+
+and edges
+\begin{equation*}
+    E = \left\{ 1 \to 2, 1 \to 3, 1 \to 4, 2 \to 1, 2 \to 3, 3 \to 4, 4 \to 1, 4 \to 3, 4 \to 5, 4 \to 6, 5 \to 6, 6 \to 5 \right\}
+\end{equation*}
+
+The directed graph for this vertex set $V$ and edge set $E$ is
+
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}
+    \coordinate (vertex1) at (4,0);
+    \coordinate (vertex2) at (2,3.464102);
+    \coordinate (vertex3) at (-2,3.464102);
+    \coordinate (vertex4) at (-4,0);
+    \coordinate (vertex5) at (-2,-3.464102);
+    \coordinate (vertex6) at (2,-3.464102);
+    %
+    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
+    %
+    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
+    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
+    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
+    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
+    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
+    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
+    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
+    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
+\end{tikzpicture}
+\end{figure}
+
+\section{A Particle in 3D}
+
+A particle in 3D has mass $m$ and is in the potential $V(x,y,z) = \frac{1}{2} m \omega^2 \left( x^2 + y^2 + z^2 \right).$
+
+\subsection{Energies of the Lowest Four Eigenstates}
+
+Suppose we need to find the energies of the four lowest eigenstates of the Hamiltonian and their corresponding degeneracies. We can start by expanding the potential as
+\begin{equation*}
+    V(x, y, z) = \underbrace{\frac{1}{2} m \omega^2 x^2}_{V_x(x)} + \underbrace{\frac{1}{2} m \omega^2 y^2}_{V_y(y)} + \underbrace{\frac{1}{2} m \omega^2 z^2}_{V_z(z)}.
+\end{equation*}
+
+And the total eigenenergy is
+\begin{equation}
+    E_{n_x n_y n_z} = E_{n_x} + E_{n_y} + E_{n_z} = \hbar \omega \left( n_x + \frac{1}{2} \right) + \hbar \omega \left( n_y + \frac{1}{2} \right) + \hbar \omega \left( n_z + \frac{1}{2} \right) \label{eq:3dQHO:eigenenergy}
+\end{equation}
+
+where $n_x, n_y, n_z = 0, 1, 2, \dots$ are independent from each other. The ground state should have $n_x = n_y = n_z = 0$, so its energy is given by
+
+\begin{equation*}
+    E_{000} = 3 \hbar \omega \left( \frac{1}{2} \right) = \frac{3}{2} \hbar \omega.
+\end{equation*}
+
+The first excited state has energy
+\begin{equation*}
+    \underbrace{E_{100} = E_{010} = E_{001}}_{\text{degeneracy 3}} = \frac{\hbar}{\omega} \left( \frac{3}{2} + \frac{1}{2} + \frac{1}{2} \right) = \frac{5}{2} \hbar \omega.
+\end{equation*}
+
+The second excited state has energy
+\begin{equation*}
+    \underbrace{E_{200} = E_{020} = E_{002} = E_{110} = E_{101} = E_{011}}_{\text{degeneracy 6}} = \frac{\hbar}{\omega} \left( \frac{5}{2} + \frac{1}{2} + \frac{1}{2} \right) = \frac{7}{2} \hbar \omega.
+\end{equation*}
+
+And finally, the third excited state has energy
+\begin{equation*}
+    \underbrace{\left\{ \begin{array}{l} E_{300} = E_{030} = E_{003} = E_{111} = E_{102} \\[0.4em] E_{120} = E_{201} = E_{021} = E_{210} = E_{012} \end{array} \right\}}_{\text{degeneracy 10}} = \frac{\hbar}{\omega} \left( \frac{7}{2} + \frac{1}{2} + \frac{1}{2} \right) = \frac{9}{2} \hbar \omega.
+\end{equation*}
+
+These results are summarized in the table below.
+
+\begin{table}[H]
+\centering
+\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\caption{Energies and corresponding degeneracies of the 3D QHO}
+\begin{tabular}{@{}ccc@{}}
+\toprule
+State & Energy & Degeneracy \\ \midrule
+\multicolumn{1}{c|}{Ground state} & \multicolumn{1}{c|}{$\displaystyle \frac{3}{2}\hbar\omega$} & 1 \\[1em]
+\multicolumn{1}{c|}{First excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{5}{2}\hbar\omega$} & 3 \\[1em]
+\multicolumn{1}{c|}{Second excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{7}{2}\hbar\omega$} & 6 \\[1em]
+\multicolumn{1}{c|}{Third excited state} & \multicolumn{1}{c|}{$\displaystyle \frac{9}{2}\hbar\omega$} & 10 \\ \bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Degeneracy of an Arbitrary Excited State}
+
+Now suppose we need to find the degeneracy $g_n$ of the $n^{th}$ excited state as a function of $n$. For our three-dimensional harmonic oscillator, we can define
+\begin{equation*}
+    n = n_x + n_y + n_z.
+\end{equation*}
+
+It follows from Eq.
+(\ref{eq:3dQHO:eigenenergy}) that the energy is strictly a function of $n$.
+That is, any combination of $n_x$, $n_y$, and $n_z$, as long as they produce the same $n$, will yield the same energy.
+Such states are said to be \emph{degenerate}.
+Our goal is to find how many possible combinations of $n_x$, $n_y$, and $n_z$ exist for a given $n$.
+
+To explicitly determine the degeneracy $g_n$ for a given state, we fix the value of $n$.
+Because of the restriction imposed by setting $n = n_x + n_y + n_z$, we really have two free parameters (say, $n_x$ and $n_y$).
+We let $n_x$ assume any allowable integer value:
+\begin{equation*}
+    n_x \in \left\{ 0, 1, \dots, n \right\}.
+\end{equation*}
+
+Then $n_y$ can assume any integer value given the sum $n_x + n_y$ does not exceed $n$:
+\begin{equation*}
+    n_y \in \left\{ 0, 1, \dots, n - n_x \right\}.
+\end{equation*}
+
+In particular, for any value of $n_x$, there are $n - n_x + 1$ unique choices for $n_y$ (note the size of the set of permissible $n_y$ values). Finally, $n_z$ is automatically fixed:
+\begin{equation*}
+    n_z = n - n_x - n_y.
+\end{equation*}
+
+For each permissible value of $n_x$ (from $0$ to $n$), there are $n - n_x + 1$ choices for $n_y$. Summing the number of these choices for all allowable values of $n_x$ yields
+\begin{align*}
+    \sum\limits_{n_x = 0}^n \left( n - n_x + 1 \right) &= \left(n + 1\right) + n + \left(n - 2\right) + \cdots + \cancelto{0}{\left(n - n\right)} \\
+                                                       &= \frac{\left(n+1\right) \left(n+2\right)}{2}.
+\end{align*}
+
+The series above is well known. Thus, we find that the degeneracy is
+\begin{equation*}
+    g_n = \frac{\left(n+1\right) \left(n+2\right)}{2}.
+\end{equation*}
+
 \end{document}

### 2021-09-06 report/chapters/opening.tex
more memes and finished serious changes

\documentclass[class=report,crop=false]{standalone}
\usepackage[margin=2.5cm,headsep=0.5cm]{geometry}
\input{../../preamblex}

\begin{document}

\section{An Opening Section}

\blindtext[5]

\begin{equation}
    x = 63
\end{equation}

\blindtext[1]

\begin{equation}
    z = 6
\end{equation}

\blindtext[1]

\begin{equation}
    w = 1986
\end{equation}

\blindtext[1]

\section{Continuing Forward}

\blindtext[5]

\begin{equation}
    y = 4
\end{equation}

\blindtext[1]

\begin{equation}
    a = 63
\end{equation}

\blindtext[1]

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=0.5]
    \fill[PURPLE] (0,0) circle (4);
\end{tikzpicture}
\caption{Here's an example figure.}
\end{figure}

\blindtext[1]

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=0.5]
    \fill[GREEN] (0,0) circle (4);
\end{tikzpicture}
\caption{Look at this! Another example figure!}
\end{figure}

\blindtext[1]

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=0.5]
    \fill[ORANGE] (0,0) circle (4);
\end{tikzpicture}
\caption{A little hard to believe. Another example figure?}
\end{figure}

\blindtext[1]

\begin{equation}
    c = 660
\end{equation}

\blindtext[1]

\begin{equation}
    t = 4
\end{equation}

\blindtext[1]

\begin{equation}
    d = 175
\end{equation}

\blindtext[5]

\section{More Explanation}

\blindtext[5]

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=0.5]
    \fill[BLUE] (0,0) circle (4);
\end{tikzpicture}
\caption{Is it true? Another example figure?}
\end{figure}

\blindtext[5]

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=0.5]
    \fill[RED] (0,0) circle (4);
\end{tikzpicture}
\caption{It looks to be another example figure.}
\end{figure}

\blindtext[5]

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=0.5]
    \fill[GOLDE] (0,0) circle (4);
\end{tikzpicture}
\caption{This has to be the last figure.}
\end{figure}

\section{Mobility}

\blindtext[5]

\begin{equation}
    f = 002
\end{equation}

\blindtext[1]

\begin{equation}
    g = 10
\end{equation}

\blindtext[5]

\subsection{Stability}

\blindtext[5]

\begin{equation}
    h = 5
\end{equation}

\blindtext[1]

\begin{equation}
    k = 20
\end{equation}

\blindtext[5]

\section{Closing}

\blindtext[5]

\begin{equation}
    h = 5
\end{equation}

\blindtext[1]

\begin{equation}
    k = 20
\end{equation}

\blindtext[1]

\begin{equation}
    u = 3
\end{equation}

\blindtext[1]

\begin{equation}
    t = 3
\end{equation}

\blindtext[10]

\end{document}

### 2022-02-03 articles/good_practice.tex
serious changes underway
cleaning up
unironically bloat
oof
close error log with le
future proofing good practice
holding
big changes coming soon

@@
 
+% Number equations within sections
+\numberwithin{equation}{section}
+
 % Continuous per-section numbering of figures and tables
@@
 \author{Nicholas D. Kostin}
-\date{October 2021}
+\date{March 2022}
 
@@
 \rhead{Nicholas D. Kostin}
-\lfoot{\texttt{https://nkostin.xyz}}
+\lfoot{\texttt{https://nkostin.com}}
 \rfoot{\thepage\ of \pageref{LastPage}}
@@
 
-This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist.
-Instead, what follows is an incoherent collection of examples that illustrate good practice.
+This document is not a guide on how to use {\LaTeX}, since plenty of those already exist.
+Instead, what follows is an incoherent collection of examples that demonstrate good practice.
 For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

### 2022-03-07 articles/good_practice.tex
fixing colors one by one
still compiles lmao
it is Wednesday my dudes
it is Wednesday my dudes aaaaaaaaaagh
changed eq to eqn

@@
 This document is not a guide on how to use {\LaTeX}, since plenty of those already exist.
-Instead, what follows is an incoherent collection of examples that demonstrate good practice.
+Instead, what follows is an incoherent collection of examples that illustrate good practice.
 For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.
@@
 \begin{equation}
-    A \ket{a} = a \ket{a}. \label{eq:quantum:eigenvalueproblem}
+    A \ket{a} = a \ket{a}. \label{eqn:quantum:eigenvalueproblem}
 \end{equation}
@@
 \begin{equation}
-    \braket{a|A|a} = \braket{a|a|a} = a\braket{a|a}. \label{eq:quantum:1}
+    \braket{a|A|a} = \braket{a|a|a} = a\braket{a|a}. \label{eqn:quantum:1}
 \end{equation}
 
-Taking the Hermitian conjugate of both sides of (\ref{eq:quantum:eigenvalueproblem}) gives
+Taking the Hermitian conjugate of both sides of (\ref{eqn:quantum:eigenvalueproblem}) gives
 \begin{equation}
@@
 \begin{equation}
-    \braket{a|A^{\dagger}|a} = a^{*} \braket{a|a} \label{eq:quantum:2}
+    \braket{a|A^{\dagger}|a} = a^{*} \braket{a|a} \label{eqn:quantum:2}
 \end{equation}
 
-Since $A$ is Hermitian, we have $\braket{a|A^{\dagger}|a} = \braket{a|A|a}$. Then comparing (\ref{eq:quantum:1}) and (\ref{eq:quantum:2}) gives
+Since $A$ is Hermitian, we have $\braket{a|A^{\dagger}|a} = \braket{a|A|a}$. Then comparing (\ref{eqn:quantum:1}) and (\ref{eqn:quantum:2}) gives
 \begin{equation*}
@@
     % Draw outside rectangle
-    \draw[black] (-2,-2) rectangle (14,10);
+    \draw[BLACK] (-2,-2) rectangle (14,10);
     % Draw lattice points
@@
     %
-    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
-    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
-    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
-    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
-    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
-    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
-    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
-    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
+    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV2);
+    \draw[BLACK, ultra thick, ->] (nodeV2) -- (nodeV3);
+    \draw[BLACK, ultra thick, <->] (nodeV3) -- (nodeV4);
+    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV5);
+    \draw[BLACK, ultra thick, <->] (nodeV5) -- (nodeV6);
+    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV4);
+    \draw[BLACK, ultra thick, ->] (nodeV1) -- (nodeV3);
+    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV6);
 \end{tikzpicture}
@@
 \begin{equation}
-    E_{n_x n_y n_z} = E_{n_x} + E_{n_y} + E_{n_z} = \hbar \omega \left( n_x + \frac{1}{2} \right) + \hbar \omega \left( n_y + \frac{1}{2} \right) + \hbar \omega \left( n_z + \frac{1}{2} \right) \label{eq:3dQHO:eigenenergy}
+    E_{n_x n_y n_z} = E_{n_x} + E_{n_y} + E_{n_z} = \hbar \omega \left( n_x + \frac{1}{2} \right) + \hbar \omega \left( n_y + \frac{1}{2} \right) + \hbar \omega \left( n_z + \frac{1}{2} \right) \label{eqn:3dQHO:eigenenergy}
 \end{equation}
@@
 It follows from Eq.
-(\ref{eq:3dQHO:eigenenergy}) that the energy is strictly a function of $n$.
+(\ref{eqn:3dQHO:eigenenergy}) that the energy is strictly a function of $n$.
 That is, any combination of $n_x$, $n_y$, and $n_z$, as long as they produce the same $n$, will yield the same energy.

### 2022-03-25 articles/good_practice.tex
new css colors working

@@
 \begin{figure}[H]
-\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
 \centering
 \begin{tikzpicture}[scale=1.1]
-    \draw[BLACK, ->] (-4,0) -- (9,0) node[BLACK, anchor=west] {$z$};
-    \draw[BLACK, ->] (0,-1.4) -- (0,1.4) node[BLACK, anchor=south] {$g(z,0)$};
-    \draw[BLUE, thick] (-4.6,1) cos (-3.6,0);
-    \draw[BLUE, thick] (-3.6,0) sin (-2.6,-1);
-    \draw[BLUE, thick] (-2.6,-1) cos (-1.6,0);
-    \draw[BLUE, thick] (-1.6,0) sin (-0.6,1);
-    \draw[BLUE, thick] (-0.6,1) cos (0.6,0);
-    \draw[BLUE, thick] (0.6,0) sin (1.6,-1);
-    \draw[BLUE, thick] (1.6,-1) cos (2.6,0);
-    \draw[BLUE, thick] (2.6,0) sin (3.6,1);
-    \draw[BLUE, thick] (3.6,1) cos (4.6,0);
-    \draw[BLUE, thick] (4.6,0) sin (5.6,-1);
-    \draw[BLUE, thick] (5.6,-1) cos (6.6,0);
-    \draw[BLUE, thick] (6.6,0) sin (7.6,1);
+    \draw[black, ->] (-4,0) -- (9,0) node[black, anchor=west] {$z$};
+    \draw[black, ->] (0,-1.4) -- (0,1.4) node[black, anchor=south] {$g(z,0)$};
+    \draw[blue, thick] (-4.6,1) cos (-3.6,0);
+    \draw[blue, thick] (-3.6,0) sin (-2.6,-1);
+    \draw[blue, thick] (-2.6,-1) cos (-1.6,0);
+    \draw[blue, thick] (-1.6,0) sin (-0.6,1);
+    \draw[blue, thick] (-0.6,1) cos (0.6,0);
+    \draw[blue, thick] (0.6,0) sin (1.6,-1);
+    \draw[blue, thick] (1.6,-1) cos (2.6,0);
+    \draw[blue, thick] (2.6,0) sin (3.6,1);
+    \draw[blue, thick] (3.6,1) cos (4.6,0);
+    \draw[blue, thick] (4.6,0) sin (5.6,-1);
+    \draw[blue, thick] (5.6,-1) cos (6.6,0);
+    \draw[blue, thick] (6.6,0) sin (7.6,1);
     %
-    \draw[BLACK, ->] (3.6,0) -- (3.6,1) node[BLACK, left, midway] {\small $A$};
-    \draw[BLACK] (3.2,1) -- (4.0,1);
+    \draw[black, ->] (3.6,0) -- (3.6,1) node[black, left, midway] {\small $A$};
+    \draw[black] (3.2,1) -- (4.0,1);
     %
-    \filldraw[BLACK] (-0.6,1) circle (0.1);
-    \node[BLACK, above] at (-3.6,1.3) {\parbox[c]{0.2\textwidth}{\begin{center} \small Central \\ maximum \end{center}}};
-    \draw[BLACK, thick, <-] (-0.7,1.1) -- (-3,2);
+    \filldraw[black] (-0.6,1) circle (0.1);
+    \node[black, above] at (-3.6,1.3) {\parbox[c]{0.2\textwidth}{\begin{center} \small Central \\ maximum \end{center}}};
+    \draw[black, thick, <-] (-0.7,1.1) -- (-3,2);
     %
-    \draw[BLACK, dashed] (-0.6,1) -- (-0.6,0);
-	\draw[BLACK, thick, decoration={brace, mirror, raise=5pt}, decorate] (-0.6,0) -- (0,0) node[black, midway, below=6pt] {\small $\delta/k$};
+    \draw[black, dashed] (-0.6,1) -- (-0.6,0);
+	\draw[black, thick, decoration={brace, mirror, raise=5pt}, decorate] (-0.6,0) -- (0,0) node[black, midway, below=6pt] {\small $\delta/k$};
 	%
-	\draw[BLACK, ->] (5,1.6) -- (6.6,1.6) node[BLACK, midway, above] {\small $v$};
+	\draw[black, ->] (5,1.6) -- (6.6,1.6) node[black, midway, above] {\small $v$};
 	%
-	\draw[BLACK] (1.6,-1) -- (1.6,-1.5);
-	\draw[BLACK] (5.6,-1) -- (5.6,-1.5);
-	\draw[BLACK, <->] (1.6,-1.25) -- (5.6,-1.25) node[BLACK, midway, below] {\small $\lambda$};
+	\draw[black] (1.6,-1) -- (1.6,-1.5);
+	\draw[black] (5.6,-1) -- (5.6,-1.5);
+	\draw[black, <->] (1.6,-1.25) -- (5.6,-1.25) node[black, midway, below] {\small $\lambda$};
 \end{tikzpicture}
@@
 \begin{figure}[H]
-\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
 \centering
@@
     % Draw outside rectangle
-    \draw[BLACK] (-2,-2) rectangle (14,10);
+    \draw[black] (-2,-2) rectangle (14,10);
     % Draw lattice points
@@
         {
-            \filldraw[BLACK] (\a, \b) circle (2pt);
+            \filldraw[black] (\a, \b) circle (2pt);
         }
     }
-    \node[BLACK, anchor=north] at (0,0) {$x_0$};
-    \node[BLACK, anchor=north] at (1,0) {$x_1$};
-    \node[BLACK, anchor=north] at (11,0) {$x_{N - 1}$};
-    \node[BLACK, anchor=north] at (12,0) {$x_N$};
-    \node[BLACK, anchor=east] at (0,0) {$y_0$};
-    \node[BLACK, anchor=east] at (0,1) {$y_1$};
-    \node[BLACK, anchor=east] at (0,7) {$y_{M - 1}$};
-    \node[BLACK, anchor=east] at (0,8) {$y_M$};
-    \draw[BLACK, <->] (7,-0.2) -- (8,-0.2);
-    \node[BLACK, below] at (7.5,-0.2) {$h$};
-    \draw[BLACK, <->] (-0.2,4) -- (-0.2,5);
-    \node[BLACK, left] at (-0.2,4.5) {$h$};
-    \filldraw[RED] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
-    \draw[RED] (6,3) -- (6,4) -- (6,5);
-    \draw[RED] (5,4)-- (6,4) -- (7,4);
-    \filldraw[BLUE] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
-    \filldraw[BLUE] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
-    \filldraw[BLUE] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
-    \filldraw[BLUE] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
-    \draw[BLACK, <->] (0,8.3) -- (12,8.3);
-    \node[BLACK, above] at (6,8.3) {$w$};
-    \draw[BLACK, <->] (12.3,0) -- (12.3,8);
-    \node[BLACK, right] at (12.3,4) {$\ell$};
+    \node[black, anchor=north] at (0,0) {$x_0$};
+    \node[black, anchor=north] at (1,0) {$x_1$};
+    \node[black, anchor=north] at (11,0) {$x_{N - 1}$};
+    \node[black, anchor=north] at (12,0) {$x_N$};
+    \node[black, anchor=east] at (0,0) {$y_0$};
+    \node[black, anchor=east] at (0,1) {$y_1$};
+    \node[black, anchor=east] at (0,7) {$y_{M - 1}$};
+    \node[black, anchor=east] at (0,8) {$y_M$};
+    \draw[black, <->] (7,-0.2) -- (8,-0.2);
+    \node[black, below] at (7.5,-0.2) {$h$};
+    \draw[black, <->] (-0.2,4) -- (-0.2,5);
+    \node[black, left] at (-0.2,4.5) {$h$};
+    \filldraw[red] (6,4) circle (2.5pt) node[anchor=south west] {$V_{n,m}$};
+    \draw[red] (6,3) -- (6,4) -- (6,5);
+    \draw[red] (5,4)-- (6,4) -- (7,4);
+    \filldraw[blue] (7,4) circle (2.5pt) node[anchor=north west] {$V_{n+1,m}$};
+    \filldraw[blue] (5,4) circle (2.5pt) node[anchor=south east] {$V_{n-1,m}$};
+    \filldraw[blue] (6,3) circle (2.5pt) node[anchor=north] {$V_{n,m+1}$};
+    \filldraw[blue] (6,5) circle (2.5pt) node[anchor=south] {$V_{n,m-1}$};
+    \draw[black, <->] (0,8.3) -- (12,8.3);
+    \node[black, above] at (6,8.3) {$w$};
+    \draw[black, <->] (12.3,0) -- (12.3,8);
+    \node[black, right] at (12.3,4) {$\ell$};
 \end{tikzpicture}
@@
     % primary colors
-    \fill[BLUE] (30:2.4) circle (4);
-    \fill[RED] (150:2.4) circle (4);
-    \fill[GREEN] (270:2.4) circle (4);
+    \fill[blue] (30:2.4) circle (4);
+    \fill[red] (150:2.4) circle (4);
+    \fill[lime] (270:2.4) circle (4);
     % secondary colors
@@
         \clip (150:2.4) circle (4);
-        \fill[PURPLE] (30:2.4) circle (4);
+        \fill[magenta] (30:2.4) circle (4);
     \end{scope}
@@
         \clip (270:2.4) circle (4);
-        \fill[YELLOW] (150:2.4) circle (4);
+        \fill[yellow] (150:2.4) circle (4);
     \end{scope}
@@
         \clip (30:2.4) circle (4);
-        \fill[TEAL] (270:2.4) circle (4);
+        \fill[cyan] (270:2.4) circle (4);
     \end{scope}
@@
         \clip (150:2.4) circle (4);
-        \fill[WHITE] (270:2.4) circle (4);
+        \fill[white] (270:2.4) circle (4);
     \end{scope}
@@
 Here are some cool circled numbers.
-The first argument is whatever is to be circled, and the \colorbox{TEAL}{second argument} is the background color.
-The \colorbox{PURPLE}{third argument} is the outline color, and the \colorbox{RED}{fourth argument} is color of the first argument.
+The first argument is whatever is to be circled, and the \colorbox{cyan}{second argument} is the background color.
+The \colorbox{purple}{third argument} is the outline color, and the \colorbox{red}{fourth argument} is color of the first argument.
 
 \begin{figure}[H]
-\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
 \centering
@@
     {
-        \node at (\c,0) {\Huge\circled{\c}{TEAL}{PURPLE}{RED}};
+        \node at (\c,0) {\Huge\circled{\c}{cyan}{purple}{red}};
     }
@@
 \begin{equation*}
-    \bigints_{\circled{$a$}{PINK}{BLACK}{BLACK}}^{\circled{$b$}{GOLDC}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{GOLDC}{BLACK}{BLACK}}^{\circled{$a$}{PINK}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{GREEN}{RED}{BLACK}}
+    \bigints_{\circled{$a$}{pink}{black}{black}}^{\circled{$b$}{goldenrod}{black}{black}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{goldenrod}{black}{black}}^{\circled{$a$}{pink}{black}{black}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{lime}{red}{black}}
 \end{equation*}
@@
     %
-    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
-    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
+    \node at (vertex1) (nodeV1) {\Huge\circled{1}{orange}{red}{nkostincolor}};
+    \node at (vertex2) (nodeV2) {\Huge\circled{2}{orange}{red}{nkostincolor}};
+    \node at (vertex3) (nodeV3) {\Huge\circled{3}{orange}{red}{nkostincolor}};
+    \node at (vertex4) (nodeV4) {\Huge\circled{4}{orange}{red}{nkostincolor}};
+    \node at (vertex5) (nodeV5) {\Huge\circled{5}{orange}{red}{nkostincolor}};
+    \node at (vertex6) (nodeV6) {\Huge\circled{6}{orange}{red}{nkostincolor}};
     %
-    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV2);
-    \draw[BLACK, ultra thick, ->] (nodeV2) -- (nodeV3);
-    \draw[BLACK, ultra thick, <->] (nodeV3) -- (nodeV4);
-    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV5);
-    \draw[BLACK, ultra thick, <->] (nodeV5) -- (nodeV6);
-    \draw[BLACK, ultra thick, <->] (nodeV1) -- (nodeV4);
-    \draw[BLACK, ultra thick, ->] (nodeV1) -- (nodeV3);
-    \draw[BLACK, ultra thick, ->] (nodeV4) -- (nodeV6);
+    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
+    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
+    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
+    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
+    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
+    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
+    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
+    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
 \end{tikzpicture}
@@
 \centering
-\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
+\captionsetup{width=0.8\textwidth,labelfont={color=black,bf},textfont={color=black}}
 \caption{Energies and corresponding degeneracies of the 3D QHO}

### 2022-03-27 articles/good_practice.tex
minor changes
I have been meaning to do this for a long time

@@
 \input{../preamblex}
+
+% No auto-indent
+\setlength{\parindent}{0pt}
 
@@
 
-\begin{theorem}[Bolzano-Weierstrass]
+\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline = false, leftline = false, rightline = false, frametitle = {Bolzano-Weierstrass Theorem}]
 Every bounded sequence has a convergent subsequence.
-\end{theorem}
+\end{mdframed}
 
@@
 
-\begin{lemma}
+\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline = false, leftline = false, rightline = false, frametitle = {Lemma}]
 Cauchy sequences are bounded.
-\end{lemma}
+\end{mdframed}
 

### 2022-03-27 article/article.tex
renamed directory
fixed whitespace problem

--- 2022-03-25 articles/good_practice.tex
@@
 \author{Nicholas D. Kostin}
-\date{March 2022}
+\date{May 2022}
 
@@
 
-\begin{theorem}[Bolzano-Weierstrass]
+\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline=false, leftline=false, rightline=false, frametitle={Bolzano-Weierstrass Theorem}]
 Every bounded sequence has a convergent subsequence.
-\end{theorem}
+\end{mdframed}
 
@@
 
-\begin{lemma}
+\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline=false, leftline=false, rightline=false, frametitle={Lemma}]
 Cauchy sequences are bounded.
-\end{lemma}
+\end{mdframed}
 
